COG-ED Manuscript

### 2022-01-07 06_Paper/COG-ED/Manuscript.Rmd
updated csl file

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : ref_COG-ED.bib
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
editor_options: 
  markdown: 
    wrap: sentence
---

@@

The paradigm was written and presented using *Psychopy* [@Peirce2019]. We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
The R Markdown file used to analyze the data and write this document is freely available at github.com/ChScheffel/CERED.
The data can be downloaded from osf.io/vnj8x/.

>>>>

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : CERED.bib
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
editor_options: 
  markdown: 
    wrap: sentence
---

@@

The paradigm was written and presented using *Psychopy* [@Peirce2019]. We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *bayestestR* [@Makowski2019] for all our analyses.
The R Markdown file used to analyze the data and write this document is freely available at github.com/ChScheffel/CERED.
The data can be downloaded from osf.io/vnj8x/.
